The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2015-12-26 article.tex
Easier to read layout

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip

>>>>

%% Use of \listoftables is discouraged.
%%
\section*{Tables}

  \subsection*{Table 1 - A selection of key CDK modules with major changes.}
  \label{tab:modules}
  An overview of a selection of often used CDK modules with description,
  dependencies on third-party libraries, and the major changes since
  version~1.2. Depedencies between modules are depicted in Figure~\ref{fig:deps}.
  \vskip 1\baselineskip

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lp{3cm}p{3cm}l}
  \textbf{Module}            & \textbf{Description}  & \textbf{Major Changes} & \textbf{Depedencies} \\ \hline
  interfaces                 &              & & Vecmath 1.5.2 \\ \hline
  core                       &              & & Google Guava 17.0 \\ \hline % FIXME: how to add https://github.com/google/guava ?
  standard                   &              & & \\ \hline
  render                     &              & Redesigned to make it more modular and support multiple widget toolkits, like AWT and SWT. & \\ \hline
  isomorphism                &              & & \\ \hline
  atomtype                   &              & Unified approach where atom typing is separated from other algorithms. & \\ \hline
  valencycheck               &              & & \\ \hline
  ioformats                  &              & & \\ \hline
  io                         &              & The MDL molfile reader has been rewritten and supports in atom types defind in the specification. & XPP3 1.1.4c \\ \hline
  iordf                      &              & New. & Jena 2.7.4 \\ \hline
  inchi                      &              & & JNI-InChI 0.8~\cite{Spjuth2013}  \\ \hline
  libiocml                   &              & & XOM 1.2.5, CMLXOM 3.1~\cite{Murray-Rust2011} \\ \hline
  smiles                     &              & SMILES support performance and converage is greatly improved. & Beam 0.9.1 \\ \hline %FIXME add a citation
  smarts                     &              & & Beam 0.9.1 \\ \hline %FIXME add a citation
  formula                    &              & New. & \\ \hline
  fingerprint                &              & Many new fingerprint types (see text). & Apache Commons Math 3.1.1 \\ \hline
  qsar                       &              & & XOM 1.2.5, JAMA 1.0.3~\cite{Hicklin2012} \\ \hline % FIXME: find JAMA reference
  signatures                 &              & & Signatures 1.1 \\ \hline % FIXME: ask Gilleain for the reference
  qsarmolecular              &              & & \\ \hline
  log4j                      &              & & Log4j 1.2.17 \\ \hline
    \end{tabular}
    \end{minipage}

  \subsection*{Table 1 - The molecular fingerprints in CDK.}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip
